\documentclass[letterpaper,11pt]{article}

\usepackage[margin=2cm]{geometry}
\usepackage{url}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{1em}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingShort}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small{#1}} & \textit{\small #2} \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\pagenumbering{gobble}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large{Ulya Trofimovich}} & London, UK \\
                                      & E-mail: \texttt{skvadrik@gmail.com} \\
                                      & Mobile: +44 7899 602 542 \\
\end{tabular*}


\vspace{1em}

\section{Summary}
I am a C++/Linux developer with background in parsing theory and compiler construction.

\section{Skills}
  \resumeSubHeadingListStart

    \resumeSubItem{Programming languages}{C++ (proficient, C++98/C++11, over 8 years of experience),
        Haskell (basic),
        Bash (basic),
        Python (beginner),
        Assembly (reading skills, mostly x86).}
    \resumeSubItem{Operating systems}{Gentoo Linux (basic usage, over 7 years of experience).}
    \resumeSubItem{Profiling and debugging tools}{Valgrind, Perf, Strace, GDB, GCC/Clang sanitizers, Objdump, etc.}
    \resumeSubItem{Parsing tools}{lexer/parser generators, parser combinators, regular expressions.}
    \resumeSubItem{Compiler theory}{dataflow, SSA, pointer modelling, compiler optimizations.}
    \resumeSubItem{VCS}{Git.}

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Belarusian State University (BSU)}{Minsk, Belarus}
      {Bachelor's Degree in Mathematics and Systems Programming}{2008 -- 2013}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {VirusBlokAda LTD}{Minsk, Belarus}
      {Software Engineer}{Aug. 2011 -- Aug. 2014}
      \resumeItemListStart
        \resumeItem{Anti-Virus Kernel}
          {co-developed a processor emulator for x86 ISA family.
          Added emulation of specific instructions
          and wrote a tool that builds statistics on instruction usage in malware code.}
        \resumeItem{JavaScript emulator}
          {developed a lightweight ECMAScript-5.1 conforming interpreter for malware emulation in a sandboxed environment
          (written from scratch in C++ and optimized for performance).}
        \resumeItem{Malware classification system}
          {developed a fast signature-based pre-filter to the anti-virus kernel
          that classifies incoming malware samples into categories.}
        \resumeItem{Regular expression library}
          {developed an internal library for Perl5-compatible regular expressions.}
      \resumeItemListEnd

    \resumeSubheading
      {Perforce (former PRQA)}{London, UK}
      {Software Engineer}{Nov. 2017 -- Feb. 2019}
      \resumeItemListStart
        \resumeItem{Dataflow engine of a C/C++ static analyzer}
          {found and fixed numerous bugs in program modelling and transformation;
          implemented checks for coding standard compliance (CERT C, RePhrase);
          extended logging and debugging capabilities;
          helped training new members of the dataflow team.}
        \resumeItem{Analysis of multithreaded code}
          {co-developed a new component for detecting bugs in multithreaded C/C++ code,
          in particular, I worked on deadlock detection.}
        \resumeItem{Scripting}
          {wrote multiple Bash/Python/C-Reduce scripts to help automate routine tasks,
          organized a centralized repository for developer scripts and helped document them.}
        \resumeItem{Administration}
          {maintained a Gentoo server used for dataflow testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source}{}
      {Software Engineer}{2011 -- present day}
      \resumeItemListStart
        \resumeItem{RE2C lexer generator}
          {(\url{http://re2c.org})
          RE2C is a tool for generating fast lexical analyzers for C/C++
          (used by such projects as PHP and Ninja).
          Contributions:
          added Unicode support for the generated lexers,
          researched and developed efficient algorithm for submatch extraction,
          developed self-testing and self-validation tools,
          implemented numerous optimizations for speed and size of the generated code,
          updated project documentation,
          extended portability,
          fixed many bugs,
          provided help and support for RE2C users.
          }
        \resumeItem{LALR2C parser generator}
          {(\url{https://github.com/skvadrik/lalr2c})
          Developed an experimental tool in Haskell for generating very fast LALR(1) parsers for C/C++.}
        \resumeItem{Other}
          {Contributed occasional patches to open source projects such as GHC Haskell compiler, Midnight Commander, xxdiff, yasm.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Research}
  \resumeSubHeadingListStart

    \resumeSubheadingShort{Tagged Deterministic Finite Automata with Lookahead}{Feb. 2015 - Aug. 2017}
      \small{Studied efficient submatch extraction in regular expressions, POSIX disambiguation semantics,
      and their practical application to performance-oriented lexer generators like RE2C.
      Wrote a paper: \url{http://re2c.org/2017_trofimovich_tagged_deterministic_finite_automata_with_lookahead.pdf}}

  \resumeSubHeadingListEnd

\section{Fields of interest}
    \small{Compiler construction, program analysis and transformation, code generation, formal languages and automata.}

\end{document}
